---
title       : Developing Data Products - Project 1
subtitle    : 
author      : Nick Allen
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Purpose

```{r, echo=FALSE, message=FALSE}
library (ggplot2)
```

The application's purpose is to enable simple exploration of bivariate relationships in the 'mtcars' data set.  

* Motor Trend Car Road Tests
* A data frame with 32 observations on 11 variables.
* The 'mtcars' data set is available within the base R installation.

--- .class #id 

## Data Fields

```{r}
str (mtcars)
```

--- .class #id 

## Example Bivariate Relationship

```{r}
ggplot (mtcars, aes (wt, mpg)) + geom_point() + geom_smooth (method = "loess")
```

--- .class #id 

## Application Link

Check out the app yourself!

* https://farsite.shinyapps.io/Project1/
